\documentclass[letterpaper,10pt]{article}

% Packages
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}

% Add sleeker font packages (pdfLaTeX compatible)
\usepackage[T1]{fontenc}

% Option 1: Helvetica - clean, modern sans-serif (default)
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Set margins
\usepackage[left=0.3in, right=0.3in, top=0.2in, bottom=0.3in]{geometry}

% Line spacing
\renewcommand{\baselinestretch}{0.95}

% Section format - reduce spacing by half
\titleformat{\section}{\scshape\raggedright\bfseries\normalsize}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2.5pt}{1pt}

% Bullet points
\renewcommand{\labelitemi}{$\bullet$}

% Hyperlinks
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% List settings
\setlist[itemize]{leftmargin=*,itemsep=0pt,parsep=0pt,topsep=1pt,partopsep=0pt}

\begin{document}

\vspace{3 pt}
\begin{center}
    {\LARGE \textbf{Shraddha Barange}} \\[3pt]
    Boston, MA --- +1-862-882-0385 --- \href{mailto:shraddhabarange2019@gmail.com}{shraddhabarange2019@gmail.com} --- 
    \href{https://www.linkedin.com/in/shraddha-barange/}{LinkedIn} --- 
      \href{https://tinyurl.com/shraddha-barange}{Website}
\end{center}

\vspace{-5 pt}
\section{SUMMARY}
\vspace{3 pt}
\noindent Regulatory Affairs Associate (M.S. Regulatory Affairs, '25) skilled in 510(k), SaMD, and NDA support. Drafted \& validated eCTD modules, built Veeva Vault/GlobalSubmit workspaces, and coordinated cross-functional inputs and cut review cycles 40\%. Known for clean templates, data-driven dashboards, and 95\% first-pass reviews.

\vspace{3 pt}
\section{SKILLS}
\vspace{3 pt}
\noindent\textbf{Regulatory Skills:} Quality Assurance, 510(k) submissions, ICH Guidelines, CAPA, GCP, FDA Premarket Submission, Post Market Surveillance, NDA, BLA, IND Applications, 21 CFR 210\&211, GVP, cGMP regulation, eCTD, Regulatory Compliance, ISO 13485, Clinical Trial Protocol, Quality Inspection (Audits), Regulatory Writing, Drug and Medical Device Safety, Global Regulatory Strategy\\
\textbf{Technical Skills:} Microsoft Office Suite, MedDRA, 21 CFRs, Product Labeling, SOP creation, Compliance Management, Research and Literature Review, Medical Writing, Statistical analysis, Document Management, Crafting Documentation (SOPs, ICF reports), DailyMed, Hypothesis testing

\vspace{3 pt}
\section{EDUCATION}
\vspace{3 pt}
\noindent\textbf{Northeastern University} \hfill \textbf{Boston, MA, USA} \\
Master of Science, Regulatory Affairs (GPA: 3.96)  \hfill \textbf{09/2023 - 06/2025} 

\vspace{3 pt}
\noindent\textbf{SCES Indira College of Pharmacy}  \hfill \textbf{Pune, India} \\
Bachelor of Pharmacy (GPA: 3.3) \hfill \textbf{08/2018 – 07/2022} 

\vspace{3 pt}
\section{WORK EXPERIENCE}

\vspace{3 pt}
\noindent\textbf{ClinGRO Solutions} \hfill \textbf{09/2025 – Present} \\
\textbf{\textit{Clinical \& Medical Writing Volunteer}} \hfill Remote
\begin{itemize}
    
    \item Drafted and standardized \textbf{clinical documentation} including \textbf{startup guides}, \textbf{internal memos}, and \textbf{SOP summaries}, ensuring \textbf{regulatory compliance} and improving document accessibility for cross-functional project teams.

\item Expanded market presence through \textbf{strategic sponsor outreach} and \textbf{targeted content development}, creating digital marketing materials and social media posts that enhanced brand visibility and supported business development initiatives.

\item Collaborated with \textbf{clinical operations teams} to document site meeting outcomes and synthesize technical discussions into actionable reports, accelerating documentation turnaround time by \textbf{25\%} and improving stakeholder communication.

\item Identified critical \textbf{documentation gaps} and developed \textbf{standardized templates} that eliminated redundant data entry, enhanced \textbf{version control efficiency}, and streamlined site file management processes.
\end{itemize}
\vspace{3 pt}
\noindent\textbf{Tecomet, Inc.} \hfill \textbf{04/2025 – 06/2025} \\
\textit{\textbf{Regulatory Affairs Project Associate}} \hfill Boston, MA
\begin{itemize}
    \item Analyzed \textbf{MAUDE reports}, internal complaint logs and \textbf{TrackWise} deviation data to spot safety trends in FSM and KCT devices, then briefed RA leadership on FDA and EU MDR implications.
    \item Drafted and validated a \textbf{MasterControl}–hosted post-market surveillance plan and report in line with \textbf{21 CFR 803/820} and \textbf{EU MDR Articles 83–86}, boosting audit readiness and laying groundwork for future 510(k)/PMA submissions.
    \item Ran root-cause investigations using \textbf{5 Whys} and \textbf{Ishikawa diagrams} in TrackWise, then rolled out corrective actions that cut repeat deviations by 30\% and lifted first-pass review rates to 95\%.
    \item Worked closely with \textbf{QA}, \textbf{R\&D}, clinical and engineering teams to update SOPs and change-control procedures based on surveillance findings, improving document accuracy and accelerating review cycles.
\end{itemize}
\vspace{3pt}
\noindent\textbf{Husky Communicator, Northeastern University} \hfill \textbf{12/2023 – 07/2025} \\
\textit{\textbf{Vice President, Communications}} \hfill Boston, MA
\begin{itemize}
    \item Led editorial team of 15 members in producing \textbf{content} including articles and materials for academic and nonprofit clients, increasing engagement by 45\%.
    \item Established comprehensive editorial guidelines and \textbf{writing style templates} ensuring consistency with regulatory requirements and client branding standards across all communication platforms.
    \item Mentored juniors on research-to-publication workflows, \textbf{data interpretation}, and writing best practices, improving content production efficiency by 30\%.
    \item Coordinated peer review processes and quality control measures for \textbf{scientific publications} and regulatory documents.
\end{itemize}
\vspace{3pt}
\noindent\textbf{Keva Health} \hfill \textbf{07/2024 – 08/2024} \\
\textit{\textbf{Regulatory Affairs Project Coordinator Intern}} \hfill Boston, MA
\begin{itemize}
    \item Conducted comprehensive market research for innovative \textbf{remote patient monitoring (RPM)} devices, analyzing competitive landscape of 15 medical technology products to support New Product Development processes and inform regulatory pathway selection.
    \item Updated company regulatory documentation and SOPs to reflect latest product offerings and \textbf{FDA guidance}, enhancing reporting capabilities for \textbf{510(k)} and \textbf{De Novo} submission readiness.
    \item Communicated complex health information clearly across different platforms, supporting regulatory intelligence processes and translating technical requirements for cross-functional teams including engineering and clinical stakeholders.
    \item Maintained document control systems and version management protocols, ensuring compliance with \textbf{21 CFR Part 820} requirements and supporting regulatory investigation processes.
\end{itemize}

\vspace{3pt}
\noindent\textbf{Purcell Ltd} \hfill \textbf{04/2024 – 06/2024} \\
\textit{\textbf{Regulatory Affairs Intern}} \hfill Boston, MA
\begin{itemize}
    \item Led preclinical study design for Class IIb Smart Inhaler and Class III AI SaMD, ensuring TGA compliance
 \item Developed patient-friendly ICFs, adhering to ethical standards and documentation control principles
\item Crafted comprehensive clinical trial strategy with targeted endpoints for asthma and COPD patients, incorporating risk management
processes.
\end{itemize}

\vspace{3pt}
\noindent\textbf{APIs Atlas LLP} \hfill \textbf{08/2022 – 08/2023} \\
\textit{\textbf{Regulatory Data Analyst}} \hfill India
\begin{itemize}
    \item Improved data quality for pharmaceutical sales reporting by implementing data cleansing techniques and validation protocols aligned with \textbf{21 CFR Part 11} requirements, supporting regulatory compliance for \textbf{NDA} and \textbf{ANDA} submissions.
    \item Led quality control and data validation processes for chemical product information using statistical analysis tools, ensuring data integrity for regulatory reporting and post-market surveillance activities.
    \item Managed multiple regulatory compliance projects simultaneously while maintaining 99.5\% accuracy standards, applying \textbf{CAPA} methodologies and risk assessment protocols to prevent data discrepancies.
    \item Developed customized client presentations and regulatory intelligence reports, demonstrating strong technical writing skills and ability to communicate complex regulatory requirements to diverse stakeholders including QA and manufacturing teams.
\end{itemize}

\vspace{3pt}
\noindent\textbf{ELKAY Chemicals Pvt. Ltd} \hfill \textbf{08/2021 – 10/2021} \\
\textit{\textbf{Quality \& Regulatory Compliance Intern}} \hfill India
\begin{itemize}
    \item Developed and implemented SOPs for chemical stability testing protocols, ensuring FDA and EU compliance with \textbf{ICH Guidelines} and \textbf{cGMP} regulations for pharmaceutical manufacturing operations.
    \item Managed laboratory documentation systems and maintained accurate record-keeping of chemical analyses per \textbf{21 CFR Part 210/211}, supporting audit readiness and regulatory inspection preparation.
    \item Participated in testing procedures requiring precise chemical analysis and quality control, contributing to batch release decisions and ensuring product safety for regulatory submissions.
   
\end{itemize}

\vspace{3 pt}
\section{PROJECTS}
\vspace{3 pt}
\noindent\textbf{Hemophilia Therapeutic Development Portfolio} \hfill \textbf{FDA Submission • IND/NDA} \
\begin{itemize}
    \item Orchestrated an end-to-end regulatory submission package for a hemophilia therapy—drafted Pre-IND strategic plan, led IND application (Form 1571), defined Pre-NDA strategy, prepared NDA/BLA submission (Form 356h), managed promotional compliance (Form 2252), and implemented safety-labeling changes—to demonstrate comprehensive FDA submission expertise and cross-functional coordination.
\end{itemize}

\vspace{3 pt}
\noindent\textbf{Multi-Regional eCTD Submission for Fentanyl Citrate} \hfill \textbf{eCTD • Global Harmonization} \
\begin{itemize}
    \item Led assembly of electronic Common Technical Document (Modules 1–5) for fentanyl citrate across FDA, EMA and TGA, tailoring regional content and formatting requirements to harmonize global regulatory submissions and accelerate international approvals.
\end{itemize}

\vspace{3 pt}
\noindent\textbf{Comprehensive Post-Market Surveillance Program} \hfill \textbf{PMS • ISO 14971 • EU MDR} \
\begin{itemize}
    \item Designed and deployed a proactive post-market surveillance framework for Class I/II devices—developing PMS plan/report and integrating ISO 14971 risk management with FDA 21 CFR 803/820/822 and EU MDR Articles 83–86—to strengthen safety monitoring and ensure full compliance.
\end{itemize}

\vspace{3 pt}
\noindent\textbf{Medical Device Design Controls \& Validation} \hfill \textbf{21 CFR 820.30 • QMS} \
\begin{itemize}
    \item Executed the complete design control and validation lifecycle for a Class II device—creating process diagrams, traceability matrix, SOPs, risk management plan, master validation plan and IQ/OQ/PQ protocols in line with 21 CFR 820.30 and FDA guidance—ensuring robust quality system adherence.
\end{itemize}

\vspace{3 pt}
\noindent\textbf{Cybersecurity in Robotic-Assisted Surgery} \hfill \textbf{SaMD • FDA Cybersecurity} \
\begin{itemize}
    \item Analyzed FDA cybersecurity guidance and conducted risk assessments for robotic-assisted surgical systems, recommending regulatory pathways for SaMD and post-market cybersecurity management strategies to mitigate vulnerabilities in connected devices.
\end{itemize}

\vspace{3 pt}
\noindent\textbf{Pharmaceutical IP \& Regulatory Strategy} \hfill \textbf{Regulatory Exclusivity • IP Strategy} \
\begin{itemize}
    \item Evaluated the interplay between regulatory exclusivity and patent protection in the Moderna vs. Pfizer/BioNTech case—analyzing global harmonization challenges and market dynamics—to inform strategic regulatory and IP decision-making.
\end{itemize}

\vspace{3 pt}
\noindent\textbf{Comparative Regulatory Intelligence} \hfill \textbf{FDA vs EMA • Global Strategy} \
\begin{itemize}
    \item Conducted a side-by-side analysis of FDA vs. EMA approval pathways—assessing clinical trial requirements, accelerated approval mechanisms, post-approval commitments and mutual recognition agreements—to optimize global submission strategies.
\end{itemize}

\end{document}
